%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BASED ON: https://github.com/deedy/Deedy-Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Andrei}{Maximov}{\urlstyle{same}\url{https://github.com/andreimaximov}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{UC San Diego}
\descript{B.S. in Computer Science}
\location{October 2014 - Present | La Jolla, CA}
Jacobs School of Engineering \\
Provost Honors \\
\location{Cum. GPA: 3.83 / 4.0 \\ Major GPA: 4.0 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
\href{https://github.com/andreimaximov}{https://github.com/andreimaximov} \\
\href{http://andreimaximov.com}{http://andreimaximov.com} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

Advanced Data Structures \\
Algorithms \\
Operating Systems \\
Computer Architecture \\
Parallel Computing \\
Advanced Graphics \\
Neural Networks and Machine Learning \\
Calculus \\
Linear Algebra

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}

\location{Proficient}
C++ \textbullet{} Java \textbullet{} Python

\location{Experience}
Rust \textbullet{} Scala \textbullet{} Lua \textbullet{} JavaScript \textbullet{} PHP
\textbullet{} OCaml \textbullet{} C

\location{Familiar}
SQL \textbullet{} Bash

\sectionsep

\subsection{Tools}

\location{Datastores}
PostgreSQL \textbullet{} MySQL \textbullet{} Redis \textbullet{} Memcached
\textbullet{} Kafka \textbullet{} HDFS

\location{Tools}
Apache Spark \textbullet{} Apache Storm \textbullet{} Hadoop MapReduce
\textbullet{} Cascading

\location{Other}
Angular 2 \textbullet{} React \textbullet{} Git \textbullet{} Mercurial

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Facebook}
\descript{ | Software Engineering Intern }
\location{September 2017 – Present | Search Ranking Infra | Menlo Park, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed and released a stream processing platform in C++ for efficiently
approximating high weight elements in a sliding window.
\item Increased time granularity for "trending X" uses cases such as for relevance
experiments in video search using top-k features.
\item Algorithm based on ideas from
\href{http://www-cs-students.stanford.edu/~datar/papers/sicomp_streams.pdf}
{Maintaining Stream Statistics over Sliding Windows} by Datar, Gionis, Indyk, and Motwani.
\end{tightemize}
\sectionsep

\runsubsection{Quora}
\descript{ | Software Engineering Intern }
\location{June 2017 – September 2017 | Infra/Data Platform | Mountain View, CA}
\begin{tightemize}
\item Designed and built a distributed system for monitoring realtime and historic
infrastructure metrics using Scala, Apache Spark, and Kafka with improved reliability
and scalability for future growth.
\item Improved Python tooling with new disaster mitgation utilities such as MySQL query 
blacklisting.
\end{tightemize}
\sectionsep

\runsubsection{Google}
\descript{ | Software Engineering Intern }
\location{June 2016 – September 2016 | Chrome Apps | Mountain View, CA}
\begin{tightemize}
\item Developed an Object Relational Mapping abstraction for integrating the Apps
Admin SDK as a datastore into App Maker.
\item Used Java and JavaScript to create a query engine on top of the Admin SDK with
filtering and relational support.
\end{tightemize}
\sectionsep

\runsubsection{eFolder}
\descript{ | Software Developer Intern }
\location{June 2014 – May 2016 | Mountain View, CA}
\begin{tightemize}
\item Developed a reporting system based on the Lambda Architecture using Java on
Hadoop MapReduce and AWS Lambda for Kinesis stream processing.
\item Built a MapReduce abstraction with Cascading for improved data pipeline
management, schema validation, and simplified join algorithm on graph data.
\item Implemented an automated billing system using PHP and PostgreSQL
responsible for processing a majority of eFolder's revenue.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{PathTracer}
\descript{ | C++ Rendering Engine }
\begin{tightemize}
\item Developed a physically accurate rendering engine with support for Monte
Carlo global illumination, fresnel reflections/refractions, texture mapping,
glossy surfaces and that probabilistically approximates the
\href{https://en.wikipedia.org/wiki/Rendering_equation}{Rendering Equation}.
\item Utilizes \href{https://en.wikipedia.org/wiki/Bounding_volume_hierarchy}{Bounding Volume Hierarchies}
for maximum performance on complex scenes and multi-threading to parallelize
chunk rendering.
\end{tightemize}
\sectionsep

\runsubsection{Programming Puzzles}
\descript{ | C++, Python, Java }
\begin{tightemize}
\item I enjoy solving Codeforces and HackerRank programming puzzles and
learning new algorithms/data-structures in my free time.
\end{tightemize}
\sectionsep

\runsubsection{Into-It Games}
\descript{ | Game Development Startup, Lua, Java, C++ }
\begin{tightemize}
\item Developed five cross platform iOS/ Android games in high school with Lua
that reached over 100k downloads and 500k game sessions.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\begin{tabular}{rll}
2013 & Outstanding Achievement in AP Physics C - Mechanics \\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}

